StreamReduce: Processing Data Streams\\and Avoiding Work

### 2012-05-07 paper/paper.tex
another editing pass

One of the problems with MapReduce is how to
incorporate new data into an already analyzed task. MapReduce simply says to rerun
the job with the new data included. Others have solved this problem by batching data
into chunks and continuously spawning MapReduce jobs to incorporate the new data.

A simpler way to incorporate new data is to treat data not as a constant, but as a
stream. By processing data on demand, one avoids repeating work involved in reprocessing
data, can save resources
by spinning workers up and down as necessary, and ensure results are as fresh as possible
by incorporating data into the result as soon as it arrives.

@@

The remainder of this paper is organized as follows. Section~\ref{sec:relwork} provides
an overview of related work on distributed stream processing as well as dynamic and
approximate computations. Section~\ref{sec:design} details how I designed StreamReduce.
Section~\ref{sec:methodology} explains the methodology used to perform a cvase study
using StreamReduce. Section~\ref{sec:evaluation} evaluates the effectiveness of StreamReduce in the case study.
Section~\ref{sec:discussion} enumerates issues with StreamReduce's current implementation.

@@

\subsection{Data Stream Management Systems}
In their overview on data stream projects~\cite{Babcock:2002:MID:543613.543615},
a new class of data streaming applications
called \emph{Data Stream Management Systems} (\emph{DSMSes}) are discussed. StreamReduce is a type of DSMS that
includes some properties found in other systems.

@@

The Aurora system~\cite{Carney:2002:MSN:1287369.1287389} introduces the concept of
\emph{load shedding}, or compensating for
resource overload by comparing job specific quality of service metrics with target levels.

>>>>

One of the problems with MapReduce is how to
incorporate new data into an already analyzed task. MapReduce simply says to rerun
the job with the new data included. Others have solved this problem by batching data
into chunks and continuously spawning MapReduce jobs to incorporate the new data
and incrementally storing updates in an external database instead of relying on
the file system for enforcing the synchronization barrier.

A simpler way to incorporate new data is to treat data not as a constant, but as a
stream. By processing data on demand, one avoids repeating work involved in reprocessing
data, can save resources
by spinning workers up and down as necessary, and ensures results are as fresh as possible
by incorporating data into the result as soon as it arrives.

@@

The remainder of this paper is organized as follows. Section~\ref{sec:relwork} provides
an overview of related work on distributed stream processing as well as dynamic and
approximate computations. Section~\ref{sec:design} details how I designed StreamReduce.
Section~\ref{sec:methodology} explains the methodology used to perform a case study
using StreamReduce. Section~\ref{sec:evaluation} evaluates the effectiveness of StreamReduce in the case study.
Section~\ref{sec:discussion} enumerates issues with StreamReduce's current implementation.

@@

\subsection{Data Stream Management Systems}
In their overview on data stream projects~\cite{Babcock:2002:MID:543613.543615},
a new class of data streaming applications
called \emph{Data Stream Management Systems} (\emph{DSMS}es) is discussed.
StreamReduce is a type of DSMS that includes some properties found in other systems.

@@

The Aurora system~\cite{Carney:2002:MSN:1287369.1287389} introduces the concept of
\emph{load shedding}, or compensating for
resource overload by comparing job specific quality of service metrics with target levels.
StreamReduce aims to incorporate load shedding to dynamically tune jobs in the face of
impending time and resource constraints.
